### 2009-03-21 doc/storage_system/arc-storage-documentation.tex
some sentences about gateway module

    TODO: makeMountpoint, unmakeMountpoint

@@

    This interface is use to pass the user's limited credentials to the system in order to access the \emph{third-party} store for methods like \emph{get}, \emph{put} and \emph{list}. For listing files and directories, \emph{gateway} uses the user credential, whereas in the \emph{get} and \emph{put} methods system only uses the credentials to check the validity of the URLs before sending it to the user.

    From the client side \emph{createDelegation()} is called which interns initiate the \emph{CredentialDelegationInitRequest} for the service. After the successful handshake this method initiates an other request of \emph{UpdateCredentials( )}, which completes this process. Response from this interface could be \emph{done}, \emph{cannot delegate credentials, requested bartender does not supports the gateway}

@@

TODO: The Bartender can utilize gateway modules for accessing file listings and transfer URL on third-party storages. Curretly we have one implementation of a gateway module [...] A gateway module should provide these methods: [...]

TODO: a few sentences about the proxy delegation.

>>>>

@@

    From the client side \emph{createDelegation()} is called which interns initiate the \emph{CredentialDelegationInitRequest} for the service. After the successful handshake this method initiates an other request of \emph{UpdateCredentials(..)}, which completes this process. For complete details see ARC-Security-Document. Response from this interface could be \emph{done}, \emph{cannot delegate credentials, requested bartender does not supports the gateway}

@@

The Bartender can utilize gateway modules for accessing file listings and transfer URL from third-party storages. It works as an optional backend component of the Bartender service. \emph{Gateway} module is based on four basic methods \emph{get}, \emph{put}, \emph{list} and \emph{remove}. Since the task is to contact external store, which requires user to delegate the credentials so that it can communicate on behelf of the user.

In order to access the \emph{files} and \emph{directories} from the external storage system, limited user credentials are passed to the \emph{Bartender} service.  Users can also remove their \emph{credentials} from the service side. These credentials are used in the methods like \emph{get}, \emph{put}, \emph{remove} and \emph{list} of the \emph{Gateway} module. These limited credentials are not used in any type of transfer, while listing files/directories, \emph{Gateway} uses the user credential, whereas in the \emph{get} and \emph{put} methods, it only uses the credentials to check the validity of the URL(s) before sending it to the user.
% subsection implementation (end)
